Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-01-24 article/supporting_information.Rmd
+ account for species with individuals with no data + fix captions in supplementary info

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=6.5, fig.height=6.5, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Asterisks indicate the number of populations with the most support. See text for the method used to select these populations.'}
# format data
bic.buff <- laply(spp.Adegenet.LST, `[[`, 'Kstat') %>%
	c() %>% range() %>% diff %>% `*`(0.05)
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		data.frame(
			k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$Kstat), fixed=TRUE)),
			stat=unname(spp.Adegenet.LST[[i]]$Kstat),
			best_k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$stat), fixed=TRUE)),
			best_stat=unname(spp.Adegenet.LST[[i]]$stat) + bic.buff,
			asterisk_col=c('black',rep('transparent', length(spp.Adegenet.LST[[i]]$Kstat)-1)),
			Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE)
		)
	}
)
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_point(aes(y=stat, x=k)) +
		geom_point(aes(y=best_stat, x=best_k), size=4, shape=8) +
		geom_line(aes(y=stat, x=k)) +
		theme_classic() +
		xlab('Number of populations') +
		ylab('BIC') +
		facet_wrap(~ Species, ncol=6)
})
```

```{r, echo=FALSE, fig.width=6.5, fig.height=6.5, fig.cap='Distribution of populations. Each panel depicts a different species. Squares denote planning units. Points denote the location of sampled individuals. The color of each point indicates the population to which each indiviudal was assigned.'}
# define function
plotLST <- llply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		# init
		curr.pts <- filter(
			spp.sample.PTS@data,
			species==unique(spp.samples.DF$species)[i]
		) %>% mutate(
			population=spp.Adegenet.LST[[i]]$grp
		)
		# create plot
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group'), fill='transparent', color='grey10') +
			geom_point(data=curr.pts, aes_string(x='sample.longitude', y='sample.latitude', color='population'),
				alpha=0.3, size=3, position='jitter') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE))
	}
)
# render plot
do.call(
	grid.arrange,
	append(
		plotLST,
		list(ncol=6)
	)
)
```

@@

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each square represents a planning unit. The color of each planning unit panel corresponds to ordination values. Planning units with similar colors contain individiduals with similar genetic variation.')}
if (1 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(1)
```

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=6.5, fig.height=6.5, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Asterisks indicate the number of populations with the most support (see text for methodological details).'}
# format data
bic.buff <- laply(spp.Adegenet.LST, `[[`, 'Kstat') %>%
	c() %>% range() %>% diff %>% `*`(0.05)
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		data.frame(
			k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$Kstat), fixed=TRUE)),
			stat=unname(spp.Adegenet.LST[[i]]$Kstat),
			best_k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$stat), fixed=TRUE)),
			best_stat=unname(spp.Adegenet.LST[[i]]$stat) + bic.buff,
			asterisk_col=c('black',rep('transparent', length(spp.Adegenet.LST[[i]]$Kstat)-1)),
			Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE)
		)
	}
)
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_point(aes(y=stat, x=k)) +
		geom_point(aes(y=best_stat, x=best_k), size=4, shape=8) +
		geom_line(aes(y=stat, x=k)) +
		theme_classic() +
		xlab('Number of populations') +
		ylab('BIC') +
		facet_wrap(~ Species, ncol=6)
})
```

```{r, echo=FALSE, fig.width=6.5, fig.height=6.5, fig.cap='Distribution of populations. Each panel depicts a different species. Squares denote planning units. Points denote the location of sampled individuals, and their colors denote the distribution of populations. Note that points have been slightly jittered so that individuals in close proximity are visible.'}
# define function
plotLST <- llply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		# init
		curr.pts <- filter(
			spp.sample.PTS@data,
			species==unique(spp.samples.DF$species)[i]
		) %>% mutate(
			population=spp.Adegenet.LST[[i]]$grp
		)
		# create plot
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group'), fill='transparent', color='grey10') +
			geom_point(data=curr.pts, aes_string(x='sample.longitude', y='sample.latitude', color='population'),
				alpha=0.3, size=3, position='jitter') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE))
	}
)
# render plot
do.call(
	grid.arrange,
	append(
		plotLST,
		list(ncol=6)
	)
)
```

@@

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (1 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(1)
```
